Differential invariant signatures for planar Lie group transformations of images

### 2020-11-18 paper/newpaper.tex
Projective stuff

\todo[inline]{Problem here? fyyy is in MF and an invariant...}
The frame $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group parameter $ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D},$ while $\bar f_{ \bar x \bar y \bar y}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}$, and $\bar f_{ \bar x \bar x}=0$ gives $ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$ In fact, the denominator of the expression for $h$ was another invariant of $A(2)$; we label it $E$ for convenience.

@@

Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants. We choose: 
\begin{equation*}
 (\bar f_{\bar x\bar x\bar x}, \bar f_{\bar x\bar x\bar y}^2, \bar f_{\bar
 x\bar y\bar
 y})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right).
\end{equation*} 
\todo[inline]{Check J2 has squared or not}
The terms $J_1, J_2, J_3$ can be written in terms of $D$ and $E$, together
with a polynomial of degree $n$ denoted by $P_n$. 
\begin{equation*}
    J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.
\end{equation*}

>>>>

The frame $\bar f_{ \bar y \bar y \bar y} = 0$ determines the group
parameter $ h = \frac{f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2
f_{xxy} - f_y^3 f_{xxx}}{6|D|^{3/2}},$ while $\bar f_{ \bar x \bar y 
y}=0$ provides $ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y
f_{xx}}{D}$, and $\bar f_{ \bar x \bar x}=0$ gives $ g = \frac{1}{2
f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$ In fact, the
numerator of the expression for $h$ was another invariant of $A(2)$; we
label it $E$ for convenience.

@@

Having determined the frame, any function of the remaining derivatives $\bar f_{ \bar x \bar x \bar x}$, $\bar f_{ \bar x \bar x \bar y}$, and $\bar f_{ \bar y \bar y \bar y}$, as given in Equation~(\ref{eq:prolong}), provides invariants. We choose: 
\begin{equation*}
 (\bar f_{\bar x\bar x\bar x}, \bar f_{\bar x\bar x\bar y}^2, \bar f_{\bar
 x\bar y\bar
 y})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right).
\end{equation*} 
The terms $J_1, J_2, J_3$ can be written in terms of $D$ and $E$, together
with a polynomial of degree $n$ denoted by $P_n$. 
\begin{equation*}
    J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5.
\end{equation*}
